Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 PandaOverview.tex
minor scattered changes in Section 3.   unlock.

PanDA's user model is based on multitenancy and the support of at least two
types of HEP users: individual researchers and groups executing so called
`production' workflows. Users are free to submit tasks and workflows to the
PanDA WMS at any point in time, directly or via dedicated application
frameworks. Consistently, PanDA's security model is based on separation between
authentication, authorization and accounting for both single users and group of
users. Both authentication and authorization are based on digital certificates
and the X.509 standard and on the virtual organization (VO) abstraction.

@@

PanDA design supports provenance and traceability for both jobs and data.
Attributes enable provenance by linking jobs and data items, providing
information like ownership or project affiliation. States enable traceability by
providing information about the stage of the execution in which each job or data
item is or has been. Some attributes are assumed to be immutable across
execution and jobs and data items are assumed to be always in one and only one
state.

@@

The implementation of PanDA consists of several interconnected subsystems, most
of them built from off-the-shelf and Open Source components. Subsystems
communicate via dedicated API or HTTP messaging and each subsystems is
implemented by one or more modules. Databases are used to store eventful
entities like tasks, jobs and events, and to store information about sites,
resources, logs, and accounting.

The execution of specific tasks of ATLAS workflows on supercomputers involves
four main subsystems of the PanDA architecture: PanDA Server, AutoPyFactory,
PanDA Pilot, and JEDI. Figure~\ref{fig:architecture} shows a diagrammatic
representation of these subsystems' architecture. For a full list of subsystems
see Ref.~\cite{panda-wiki_url}.

@@

The AutoPyFactory subsystem communicates with the Task Buffer component of the
PanDA Server, acquiring information about jobs that are ready for execution on
specific (type of) sites (Fig.~\ref{fig:architecture}:9). On the base of this
information, AutoPyFactory defines a set of suitable PanDA Pilots and
concurrently submits them a Condor-G broker (Fig.~\ref{fig:architecture}:10).
This broker submits these pilots wrapped as jobs or VMs to the required sites
(Fig.~\ref{fig:architecture}:11).

>>>>

PanDA's user \jhanote{usage} model is based on multitenancy \jhanote{of what?}
and the support of at least two types of HEP users: individual researchers and
groups executing so called `production' workflows. Users are free to submit
tasks and workflows to the PanDA WMS at any point in time, directly or via
dedicated application frameworks. Consistently, PanDA's security model is
based on separation between authentication, authorization and accounting for
both single users and group of users. Both authentication and authorization
are based on digital certificates and the X.509 standard and on the virtual
organization (VO) abstraction.

@@

PanDA's design supports provenance and traceability for both jobs and data.
Attributes enable provenance by linking jobs and data items, providing
information like ownership or project affiliation. States enable traceability by
providing information about the stage of the execution in which each job or data
item is or has been. Some attributes are assumed to be immutable across
execution and jobs and data items are assumed to be always in one and only one
state.

@@

The implementation of PanDA consists of several interconnected subsystems, most
of them built from off-the-shelf and Open Source components. Sbub-systems
communicate via dedicated API or HTTP messaging and each sub-system is
implemented by one or more modules. Databases are used to store eventful
entities like tasks, jobs and events, and to store information about sites,
resources, logs, and accounting.

The execution of specific tasks of ATLAS workflows on supercomputers involves
four main subsystems of the PanDA architecture: PanDA Server, AutoPyFactory,
PanDA Pilot, and JEDI. Figure~\ref{fig:architecture} shows a diagrammatic
representation of these sub-systems' architecture. For a full list of subsystems
see Ref.~\cite{panda-wiki_url}.

@@

The AutoPyFactory subsystem communicates with the Task Buffer component of the
PanDA Server, acquiring information about jobs that are ready for execution on
specific (type of) sites (Fig.~\ref{fig:architecture}:9). On the basis of this
information, AutoPyFactory defines a set of suitable PanDA Pilots and
concurrently submits them to a Condor-G broker (Fig.~\ref{fig:architecture}:10).
This broker submits these pilots wrapped as jobs or VMs to the required sites
(Fig.~\ref{fig:architecture}:11).
